Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-04-22 paper/table-data.tex
experiments (autcross -T 300) - worse numbers

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\79/89 solved aut.\\236 acc.~marks}}
&
level 1 &
236 & 0.0 & 269.4 & 79 & 0
\\
&
level 2 &
236 & 0.0 & 284.4 & 79 & 0
\\
&
level 3 &
227 & 3.8 & 517.4 & 72 & 7
\\
&
multi &
227 & 3.8 & 537.4 & 73 & 6
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\103/108 solved aut.\\419 acc.~marks}}
&
level 1 &
403 & 3.8 & 658.2 & 85 & 18
\\
&
level 2 &
405 & 3.3 & 738.9 & 83 & 20
\\
&
level 3 &
397 & 5.3 & 901.5 & 78 & 25
\\
&
multi &
394 & 6.0 & 2170.6 & 78 & 25
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\153/162 solved aut.\\618 acc.~marks}}
&
level 1 &
435 & 29.6 & 788.4 & 135 & 18
\\
&
level 2 &
445 & 28.0 & 887.7 & 132 & 21
\\
&
level 3 &
451 & 27.0 & 1243.3 & 122 & 31
\\
&
multi &
423 & 31.6 & 2427.8 & 126 & 27
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\266/274 solved aut.\\972 acc.~marks}}
&
level 1 &
606 & 37.7 & 774.2 & 250 & 16
\\
&
level 2 &
617 & 36.5 & 906.6 & 246 & 20
\\
&
level 3 &
617 & 36.5 & 1101.0 & 240 & 26
\\
&
multi &
596 & 38.7 & 2285.3 & 240 & 26
\\

>>>>

\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dela}\\158/162 solved aut.\\667 acc.~marks}}
&
level 1 &
487 & 27.0 & 1148.9 & 133 & 25
\\
&
level 2 &
492 & 26.2 & 1262.6 & 132 & 26
\\
&
level 3 &
499 & 25.2 & 1701.5 & 120 & 38
\\
&
multi &
479 & 28.2 & 3521.4 & 124 & 34
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2dgra}\\274/274 solved aut.\\1084 acc.~marks}}
&
level 1 &
706 & 34.9 & 1213.1 & 249 & 25
\\
&
level 2 &
716 & 33.9 & 1416.9 & 246 & 28
\\
&
level 3 &
716 & 33.9 & 1766.9 & 240 & 34
\\
&
multi &
695 & 35.9 & 3707.9 & 241 & 33
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl2tgba}\\81/89 solved aut.\\246 acc.~marks}}
&
level 1 &
246 & 0.0 & 640.7 & 81 & 0
\\
&
level 2 &
246 & 0.0 & 691.7 & 80 & 1
\\
&
level 3 &
237 & 3.7 & 1101.5 & 73 & 8
\\
&
multi &
237 & 3.7 & 1170.3 & 74 & 7
\\
\midrule
\multirow{4}{*}{\makecell{\texttt{ltl3tela}\\107/108 solved aut.\\463 acc.~marks}}
&
level 1 &
447 & 3.5 & 932.8 & 85 & 22
\\
&
level 2 &
449 & 3.0 & 1017.0 & 83 & 24
\\
&
level 3 &
441 & 4.8 & 1183.9 & 78 & 29
\\
&
multi &
438 & 5.4 & 2973.9 & 78 & 29
\\
